paper_replication

### 2021-12-15 paper_replication.Rmd
Update paper_replication.Rmd

ggplot(df, aes(x = ps, group = inanalysislabel)) + geom_density(aes(fill = inanalysislabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")

ggplot(df, aes(x = ps, fill = inanalysislabel, color = inanalysislabel)) +
  geom_histogram(alpha = 0.3, position = 'identity', bins=15) +
  facet_grid(as.factor(inanalysis) ~ .) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  scale_color_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical')

df %>%
  mutate(ps.grp = round(ps/0.05) * 0.05) %>%
  group_by(inanalysis, ps.grp) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(n2 = ifelse(inanalysis == 0, yes = n, no =  -1*n)) %>%
  ggplot(aes(x = ps.grp, y = n2, fill = as.factor(inanalysis))) +
  geom_bar(stat = 'identity', position = 'identity') +
  geom_text(aes(label = n, x = ps.grp, y = n2 + ifelse(inanalysis == 0, 8, -8))) +
  xlab('Probability of Being in the Analysis') +
  ylab('N') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete(name = "", labels = c("Counties in States With Abortion Data", "Counties in States Without Abortion Data")) +
  scale_x_continuous(breaks = seq(0, 1, 0.05)) +
  theme(legend.position = 'bottom', legend.direction = 'vertical',
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

>>>>

ggplot(df, aes(x = ps, group = inanalysislabel)) + geom_density(aes(fill = inanalysislabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Figure 1: Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")

# ggplot(df, aes(x = ps, fill = inanalysislabel, color = inanalysislabel)) +
#   geom_histogram(alpha = 0.3, position = 'identity', bins=15) +
#   facet_grid(as.factor(inanalysis) ~ .) +
#   xlab('Probability of Being in the Analysis') +
#   ggtitle('Propensity Score Distribution by Group') +
#   scale_fill_discrete('') +
#   scale_color_discrete('') +
#   theme(legend.position = 'bottom', legend.direction = 'vertical')
# 
# df %>%
#   mutate(ps.grp = round(ps/0.05) * 0.05) %>%
#   group_by(inanalysis, ps.grp) %>%
#   summarize(n = n()) %>%
#   ungroup() %>%
#   mutate(n2 = ifelse(inanalysis == 0, yes = n, no =  -1*n)) %>%
#   ggplot(aes(x = ps.grp, y = n2, fill = as.factor(inanalysis))) +
#   geom_bar(stat = 'identity', position = 'identity') +
#   geom_text(aes(label = n, x = ps.grp, y = n2 + ifelse(inanalysis == 0, 8, -8))) +
#   xlab('Probability of Being in the Analysis') +
#   ylab('N') +
#   ggtitle('Propensity Score Distribution by Group') +
#   scale_fill_discrete(name = "", labels = c("Counties in States With Abortion Data", "Counties in States Without Abortion Data")) +
#   scale_x_continuous(breaks = seq(0, 1, 0.05)) +
#   theme(legend.position = 'bottom', legend.direction = 'vertical',
#         axis.ticks.y = element_blank(),
#         axis.text.y = element_blank())
